Disagreement Regarding 2016 Presidential Election in the United States^[Code and data are available at: https://github.com/SANGWOONG-LEE/2016electionanalysis]

### 2022-04-19 outputs/paper/paper.Rmd
test

```{r fig2,echo=FALSE,fig.cap = "Distribution of national spending on foreign aid"}
c_data$nataid <- factor(c_data$nataid,                                  
                  levels = c("Too little", "About right", "Too much"))
c_data  %>%
  drop_na(nataid)  %>%
   ggplot(aes(x= nataid,group=year)) + 
    geom_bar(aes(y = ..prop.., fill = factor(..x..))) +
    geom_text(aes( label = scales::percent(..prop..),
                   y= ..prop.. ), stat= "count", vjust = -0.4) +
    labs(x = element_blank(),y = "Percent", fill = "National Spending Level", title = "National Spending Levels by Year") +
    facet_grid(~year) +
    scale_y_continuous(labels = scales::percent) +
    scale_fill_manual(labels = c("1" = "Too little", "2" = "About right", "3" = "Too much"),
                                 values=c("#01378C","#2cd18c", "#ff3d3d"))
```

>>>>

```{r fig2,echo=FALSE,fig.cap = "Distribution of national spending on "}
c_data$nataid <- factor(c_data$nataid,                                  
                  levels = c("Too little", "About right", "Too much"))
c_data  %>%
  drop_na(nataid)  %>%
   ggplot(aes(x= nataid,group=year)) + 
    geom_bar(aes(y = ..prop.., fill = factor(..x..))) +
    geom_text(aes( label = scales::percent(..prop..),
                   y= ..prop.. ), stat= "count", vjust = -0.4) +
    labs(x = element_blank(),y = "Percent", fill = "National Spending Level", title = "National Spending Levels by Year") +
    facet_grid(~year) +
    scale_y_continuous(labels = scales::percent) +
    scale_fill_manual(labels = c("1" = "Too little", "2" = "About right", "3" = "Too much"),
                                 values=c("#01378C","#2cd18c", "#ff3d3d"))
```
